---
title: "StatEtModeleReco"
author: "Dussutour A. /Desgrez Dautet H."
date: "2023-05-17"
output: html_document
---

```{r setup, include=FALSE}
CODE=FALSE
CLEAN='hide'
```

```{r library, message=FALSE,results=FALSE,warning=FALSE, echo=CODE}
library(lme4)
library(car) 
library(multcomp)
library(ggplot2)
library(MuMIn)
library(nlme)
library(lattice)
library(MASS)
library(emmeans)
library(gridExtra)
library(sjPlot)
library(sjmisc)
library(xtable)
library("ggpubr")
library(bestNormalize)
library(gridExtra)
library(grid)
library("dplyr")
library(lmerTest)
library(ggpubr)
library(unmarked)
library(AICcmodavg)
```

#RECOVERY

#open file : Data_hermes_Recovery.txt

```{r }
#DATA_RECOVERY <- read.table(file.choose(), header = TRUE)
#str(DATA_RECOVERY)

DATA_RECOVERY <- read.csv(file.choose(), header = TRUE, sep = ";")
#summary(mainDF)
```

#plot data distribution and normality test, variable nucBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$nucBy10Mic3, 
          main = "Density plot for the number of nuclei by 1000 µm³", 
          xlab = "Number of nuclei by 1000 µm³")
ggqqplot(DATA_RECOVERY$nucBy10Mic3)
shapiro.test(DATA_RECOVERY$nucBy10Mic3)
```



#normalize variable nucBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
bestNormalize(DATA_RECOVERY$nucBy10Mic3, allow_orderNorm = FALSE)
nucBy10Mic3BN <- bestNormalize(DATA_RECOVERY$nucBy10Mic3)
MASS::truehist(DATA_RECOVERY$nucBy10Mic3)
MASS::truehist(nucBy10Mic3BN$x.t)
DATA_RECOVERY$nucBy10Mic3.t <- nucBy10Mic3BN$x.t
boxplot(log10(nucBy10Mic3BN$oos_preds), 
        yaxt = 'n')
axis(2, 
     at = log10(c(.1, .5, 1, 2, 5, 10)), 
     labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable nucBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$nucBy10Mic3.t, 
          main = "Density plot for the number of nuclei by 1000 µm³ Normalized", 
          xlab = "Number of nuclei by 1000 µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$nucBy10Mic3.t)
shapiro.test(DATA_RECOVERY$nucBy10Mic3.t)
```

#run LMM , variable nucBy10Mic3 normalized

```{r ,echo=CODE, result=CODE,message=FALSE}
ModelnucBy10Mic3 <-
   lmer(nucBy10Mic3.t ~ Awake * Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelnucBy10Mic3)
ModelnucBy10Mic3_2 <-
   lmer(nucBy10Mic3.t ~ Awake + Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelnucBy10Mic3_2)
anova(ModelnucBy10Mic3, 
      ModelnucBy10Mic3_2, 
      test = 'F')

anova(ModelnucBy10Mic3, 
      type = 3, 
      ddf = "Satterthwaite")

tab_model(ModelnucBy10Mic3,
          show.df = TRUE,
          show.stat = TRUE,
          show.loglik = TRUE,
          dv.labels = "Number of nuclei by 1000 µm³ (Normalized)",
          pred.labels = c("Intersection", 
                          "Recovery", 
                          "Lu vs Malu", 
                          "Recovery x Strain"))

```

#____________________________________________#
```{r}
anova(ModelnucBy10Mic3, 
      type = 3, 
      ddf = "Satterthwaite")
```

```{r , echo=CODE, fig.show=CLEAN}
plot(ModelnucBy10Mic3_2)
par(mfrow = c(1, 2))
qqnorm(lme4::ranef(ModelnucBy10Mic3_2)$ID2[, 1],
       main = "Random effects of ID")
qqnorm(resid(ModelnucBy10Mic3_2), 
       main = "Residuals")
```

```{r }
aggregate(nucBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(nucBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = sd)
aggregate(nucBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(nucBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = sd)
```

#Graph, variable nucBy10Mic3

```{r , message=FALSE,results=FALSE,warning=FALSE, echo=CODE}
GraphnucBy10Mic3 <-
   ggboxplot(DATA_RECOVERY,
             x = "Spec",
             y = "nucBy10Mic3",
             color = "Spec",
             palette = "jco",
             add = "jitter") + 
     labs(x = "Strain", y = "Number of nuclei by 1000 µm³") + 
     scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu")) +
     stat_summary(fun.y = mean,
                  geom = "point",
                  shape = 20,
                  size = 10,
                  color = "grey",
                  fill = "grey") + 
  theme(panel.background = element_rect(fill = "white", 
                                        colour = "black"),
        legend.position = "none",
        legend.text = element_text(size = 24),
        text = element_text(size = 24),
        plot.title = element_text(hjust = 0.5)) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + 
  plot(GraphnucBy10Mic3)
Awake.labs <- c("Before", "After")
names(Awake.labs) <- c("Before", "After")
GraphnucBy10Mic3T <- GraphnucBy10Mic3 +
     facet_grid(. ~ factor(Awake, 
                           levels = c('Before', 'After')), 
                labeller = labeller (Awake = Awake.labs)) + 
  theme(strip.background = element_rect(colour = "black"
                                        , fill = "white"))
plot(GraphnucBy10Mic3T)
```


#plot data distribution and normality test, variable meanAreaNuc

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$meanAreaNuc, 
          main = "Density plot for Mean Area of a Nucleus by 1000 µm³", 
          xlab = "Mean Area of a Nucleus")
ggqqplot(DATA_RECOVERY$meanAreaNuc)
shapiro.test(DATA_RECOVERY$meanAreaNuc)
```

#normalize variable meanAreaNuc

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
bestNormalize(DATA_RECOVERY$meanAreaNuc, allow_orderNorm = FALSE)
meanAreaNucBN <- bestNormalize(DATA_RECOVERY$meanAreaNuc)
MASS::truehist(DATA_RECOVERY$meanAreaNuc)
MASS::truehist(meanAreaNucBN$x.t)
DATA_RECOVERY$meanAreaNuc.t <- meanAreaNucBN$x.t
boxplot(log10(meanAreaNucBN$oos_preds), yaxt = 'n')
axis(2, 
     at = log10(c(.1, .5, 1, 2, 5, 10)), 
     labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable meanAreaNuc

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$meanAreaNuc.t,
          main = "Density plot for the Mean Area of a Nucleus Normalized",
          xlab = "Mean Area of a Nucleus (Normalized)")
ggqqplot(DATA_RECOVERY$meanAreaNuc.t)
shapiro.test(DATA_RECOVERY$meanAreaNuc.t)
```

#run LMM , variable meanAreaNuc normalized

```{r ,echo=CODE, result=CODE,message=FALSE}
ModelmeanAreaNuc <-
   lmer(meanAreaNuc.t ~ Awake * Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelmeanAreaNuc)
ModelmeanAreaNuc_2 <-
   lmer(meanAreaNuc.t ~ Awake + Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelmeanAreaNuc_2)
anova(ModelmeanAreaNuc, 
      ModelmeanAreaNuc_2, 
      test = 'F')

anova(ModelmeanAreaNuc, 
      type = 3, 
      ddf = "Satterthwaite")

tab_model(ModelmeanAreaNuc,
          show.df = TRUE,
          show.stat = TRUE,
          show.loglik = TRUE,
          dv.labels = "Area of a Nucleus (Normalized)",
          pred.labels = c("Intersection", 
                          "Recovery", 
                          "Lu vs Malu", 
                          "Recovery x Strain"))

```


#____________________________________________#
```{r}
anova(ModelmeanAreaNuc, 
      type = 3, 
      ddf = "Satterthwaite")
```

```{r , echo=CODE, fig.show=CLEAN}
plot(ModelmeanAreaNuc_2)
par(mfrow = c(1, 2))
qqnorm(lme4::ranef(ModelmeanAreaNuc_2)$ID2[, 1], 
       main = "Random effects of ID")
qqnorm(resid(ModelmeanAreaNuc_2), 
       main = "Residuals")
```

```{r }
aggregate(meanAreaNuc ~ Awake + Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(meanAreaNuc ~ Awake + Spec, data = DATA_RECOVERY, FUN = sd)
aggregate(meanAreaNuc ~ Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(meanAreaNuc ~ Spec, data = DATA_RECOVERY, FUN = sd)
```

#Graph, variable meanAreaNuc

```{r, message=FALSE,results=FALSE,warning=FALSE, echo=CODE}
GraphmeanAreaNuc <- ggboxplot(DATA_RECOVERY,
                              x = "Spec",
                              y = "meanAreaNuc",
                              color = "Spec",
                              palette = "jco",
                              add = "jitter") + 
  labs(x = "Strain", y = "Area of a Nucleus (µm²)") + 
  scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu")) + 
  stat_summary(fun.y = mean,
               geom = "point",
               shape = 20,
               size = 10,
               color = "grey",
               fill = "grey") + 
  theme(panel.background = element_rect(fill = "white", 
                                        colour = "black"),
        legend.position = "none",
        legend.text = element_text(size = 24),
        text = element_text(size = 24),
        plot.title = element_text(hjust = 0.5)) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+ 
  ylim(4,18) #######

theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + 
  plot(GraphmeanAreaNuc) 

Awake.labs <- c("After", "Before")

names(Awake.labs) <- c("After", "Before")

GraphmeanAreaNucT <- GraphmeanAreaNuc + 
     facet_grid(. ~ factor(Awake, 
                           levels = c('Before', 'After')), 
                labeller = labeller (Awake = Awake.labs)) + 
  theme(strip.background = element_rect(colour = "black", 
                                        fill = "white"))
plot(GraphmeanAreaNucT)
```





#plot data distribution and normality test, variable circ

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$circ, 
          main = "Density plot for circularity", 
          xlab = "Circularity")
ggqqplot(DATA_RECOVERY$circ)
shapiro.test(DATA_RECOVERY$circ)
```

#normalize variable circ

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
bestNormalize(DATA_RECOVERY$circ, allow_orderNorm = FALSE)
circBN <- bestNormalize(DATA_RECOVERY$circ)
MASS::truehist(DATA_RECOVERY$circ)
MASS::truehist(circBN$x.t)
DATA_RECOVERY$circ.t <- circBN$x.t
boxplot(log10(circBN$oos_preds), yaxt = 'n')
axis(2, 
     at = log10(c(.1, .5, 1, 2, 5, 10)), 
     labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$circ.t, 
          main = "Density plot for circularity Normalized", 
          xlab = "Circularity (Normalized)")

ggqqplot(DATA_RECOVERY$circ.t)
shapiro.test(DATA_RECOVERY$circ.t)
```

#run LMM , variable circ normalized

```{r ,echo=CODE, result=CODE,message=FALSE}
ModelCirc <- 
     lmer(circ.t ~ Awake * Spec + (1 | ID2), 
                data = DATA_RECOVERY)
summary(ModelCirc)
ModelCirc_2 <- 
     lmer(circ.t ~ Awake + Spec + (1 | ID2), 
                data = DATA_RECOVERY)
summary(ModelCirc_2)
anova(ModelCirc, 
      ModelCirc_2, 
      test = 'F')

anova(ModelCirc, 
      type = 3, 
      ddf = "Satterthwaite")

tab_model(
   ModelCirc,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Circularity (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu", "Age x Strain"))

```


#____________________________________________#
```{r}
anova(ModelCirc, 
      type = 3, 
      ddf = "Satterthwaite")
```

```{r , echo=CODE, fig.show=CLEAN}
plot(ModelCirc)
par(mfrow = c(1, 2))
qqnorm(lme4::ranef(ModelCirc)$ID2[, 1], 
       main = "Random effects of ID")
qqnorm(resid(ModelCirc), 
       main = "Residuals")
```


moyenne, écart type

```{r }
aggregate(circ ~ Awake + Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(circ ~ Awake + Spec, data = DATA_RECOVERY, FUN = sd)
aggregate(circ ~ Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(circ ~ Spec, data = DATA_RECOVERY, FUN = sd)
```

#Graph, variable circ

```{r, message=FALSE,results=FALSE,warning=FALSE,echo=CODE}
GraphCirc <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "circ",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   ) + 
  labs(x = "Strain", y = "Circularity") + 
  scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu")) + 
  stat_summary(fun.y = mean,
               geom = "point",
               shape = 20,
               size = 10,
               color = "grey",
               fill = "grey"
) + 
  theme(panel.background = element_rect(fill = "white", 
                                        colour = "black"),
        legend.position = "none",
        legend.text = element_text(size = 24),
        text = element_text(size = 24),
        plot.title = element_text(hjust = 0.5)
) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + 
  plot(GraphCirc)

Awake.labs <- c("After", "Before")
names(Awake.labs) <- c("After", "Before")
GraphCircT <- GraphCirc +
  facet_grid(. ~ factor(Awake,levels = c('Before', 'After')), 
             labeller = labeller(Awake = Awake.labs)) +
  theme(strip.background = element_rect(colour = "black",
                                        fill = "white"))
plot(GraphCircT)
```


#plot data distribution and normality test, variable MitoBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$MitoBy10Mic3, 
          main = "Density plot for the number of mitochondria by 1000 µm³",
          xlab = "Number of mitochondria by 1000 µm³")
ggqqplot(DATA_RECOVERY$MitoBy10Mic3)
shapiro.test(DATA_RECOVERY$MitoBy10Mic3)
```

#normalize variable MitoBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
bestNormalize(DATA_RECOVERY$MitoBy10Mic3, allow_orderNorm = FALSE)
MitoBy10Mic3BN <- bestNormalize(DATA_RECOVERY$MitoBy10Mic3)
MASS::truehist(DATA_RECOVERY$MitoBy10Mic3)
MASS::truehist(MitoBy10Mic3BN$x.t)
DATA_RECOVERY$MitoBy10Mic3.t <- MitoBy10Mic3BN$x.t
boxplot(log10(MitoBy10Mic3BN$oos_preds), yaxt = 'n')
axis(2, 
     at = log10(c(.1, .5, 1, 2, 5, 10)), 
     labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable MitoBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$MitoBy10Mic3.t, 
          main = "Density plot for the number of mitochondria by 1000 µm³",
          xlab = "Number of mitochondria by 1000 µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$MitoBy10Mic3.t)
shapiro.test(DATA_RECOVERY$MitoBy10Mic3.t)
```

#run LMM , variable MitoBy10Mic3 normalized

```{r ,echo=CODE, result=CODE,message=FALSE}
ModelMitoBy10Mic3 <-
   lmer(MitoBy10Mic3.t ~ Awake * Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelMitoBy10Mic3)
ModelMitoBy10Mic3_2 <-
   lmer(MitoBy10Mic3.t ~ Awake + Spec + (1 | ID2), 
              data = DATA_RECOVERY)
summary(ModelMitoBy10Mic3_2)
anova(ModelMitoBy10Mic3, 
      ModelMitoBy10Mic3_2, 
      test = 'F')

anova(ModelMitoBy10Mic3_2, 
      type = 3, 
      ddf = "Satterthwaite")

tab_model(ModelMitoBy10Mic3_2,
          show.df = TRUE,
          show.stat = TRUE,
          show.loglik = TRUE,
          dv.labels = "Number of mitochondria by 1000 µm³ (Normalized)",
          pred.labels = c("Intersection", "Recovery", "Lu vs Malu"))

```

#____________________________________________#
```{r}
anova(ModelMitoBy10Mic3, 
      type = 3, 
      ddf = "Satterthwaite")
```

```{r , echo=CODE, fig.show=CLEAN}
plot(ModelMitoBy10Mic3_2)
par(mfrow = c(1, 2))
qqnorm(lme4::ranef(ModelMitoBy10Mic3_2)$ID2[, 1], 
       main = "Random effects of ID")
qqnorm(resid(ModelMitoBy10Mic3_2), 
       main = "Residuals")
```

```{r }
aggregate(MitoBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(MitoBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = sd)
aggregate(MitoBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(MitoBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = sd)
```

#Graph, variable MitoBy10Mic3

```{r , message=FALSE,results=FALSE,warning=FALSE, echo=CODE}
GraphMitoBy10Mic3 <- ggboxplot(DATA_RECOVERY,
                             x = "Spec",
                             y = "MitoBy10Mic3",
                             color = "Spec",
                             palette = "jco",
                             add = "jitter") + 
     labs(x = "Strain", y = "Nucleoide by 1000 µm³") +
     scale_x_discrete(breaks = c("Lu", "MaLu"),
                      labels = c("Lu", "Malu")) + 
     stat_summary(fun.y = mean,
                  geom = "point",
                  shape = 20,
                  size = 10,
                  color = "grey",
                  fill = "grey") + 
  theme(panel.background = element_rect(fill = "white", 
                                        colour = "black"),
        legend.position = "none",
        legend.text = element_text(size = 24),
        text = element_text(size = 24),
        plot.title = element_text(hjust = 0.5)) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  ylim(0,500)

theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + 
  plot(GraphMitoBy10Mic3) 
Awake.labs <- c("Before", "After")
names(Awake.labs) <- c("Before", "After")
GraphMitoBy10Mic3T <- GraphMitoBy10Mic3 + 
     facet_grid(. ~ factor(Awake, 
                           levels = c('Before', 'After')), 
                labeller = labeller (Awake = Awake.labs)) + 
  theme(strip.background = element_rect(colour = "black", 
                                        fill = "white"))
plot(GraphMitoBy10Mic3T)
```


#plot data distribution and normality test, variable IntBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$IntBy10Mic3, 
          main = "Density plot for Mitosox signal by 1000 µm³", 
          xlab = "Mitosox signal by 1000 µm³")
ggqqplot(DATA_RECOVERY$IntBy10Mic3)
shapiro.test(DATA_RECOVERY$IntBy10Mic3)
```

#normalize variable IntBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
bestNormalize(DATA_RECOVERY$IntBy10Mic3, allow_orderNorm = FALSE)
IntBy10Mic3BN <- bestNormalize(DATA_RECOVERY$IntBy10Mic3)
MASS::truehist(DATA_RECOVERY$IntBy10Mic3)
MASS::truehist(IntBy10Mic3BN$x.t)
DATA_RECOVERY$IntBy10Mic3.t <- IntBy10Mic3BN$x.t
boxplot(log10(IntBy10Mic3BN$oos_preds), yaxt = 'n')
axis(2, 
     at = log10(c(.1, .5, 1, 2, 5, 10)), 
     labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntBy10Mic3

```{r , message=FALSE,results=FALSE,echo=CODE, fig.show=CLEAN}
ggdensity(DATA_RECOVERY$IntBy10Mic3.t, 
          main = "Density plot for the Mitosox signal by 1000 µm³ Normalized", 
          xlab = "Mitosox signal by 1000 µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$IntBy10Mic3.t)
shapiro.test(DATA_RECOVERY$IntBy10Mic3.t)
```

#run LMM , variable IntBy10Mic3 normalized

```{r ,echo=CODE, result=CODE,message=FALSE}
ModelIntBy10Mic3 <-
   lmer(IntBy10Mic3.t ~ Awake * Spec + (1 | ID2), 
              data = DATA_RECOVERY)

summary(ModelIntBy10Mic3)

ModelIntBy10Mic3_2 <-
   lmer(IntBy10Mic3.t ~ Awake + Spec + (1 | ID2), 
              data = DATA_RECOVERY)

summary(ModelIntBy10Mic3_2)

anova(ModelIntBy10Mic3, ModelIntBy10Mic3_2, test = 'F')

anova(ModelIntBy10Mic3, type = 3, ddf = "Satterthwaite")

tab_model(ModelIntBy10Mic3,
          show.df = TRUE,
          show.stat = TRUE,
          show.loglik = TRUE,
          dv.labels = "Mitosox signal by 1000 µm³ (Normalized)",
          pred.labels = c("Intersection", 
                          "Recovery", 
                          "Lu vs Malu"))

```

#____________________________________________#
```{r}
anova(ModelIntBy10Mic3, 
      type = 3, 
      ddf = "Satterthwaite")
```

```{r , echo=CODE, fig.show=CLEAN}
plot(ModelIntBy10Mic3)

par(mfrow = c(1, 2))
qqnorm(lme4::ranef(ModelIntBy10Mic3)$ID2[, 1],
       main = "Random effects of ID")

qqnorm(resid(ModelIntBy10Mic3), 
       main = "Residuals")
```

```{r }
aggregate(IntBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(IntBy10Mic3 ~ Awake + Spec, data = DATA_RECOVERY, FUN = sd)
aggregate(IntBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = mean)
aggregate(IntBy10Mic3 ~ Spec, data = DATA_RECOVERY, FUN = sd)
```

#Graph, variable IntBy10Mic3

```{r , message=FALSE,results=FALSE,warning=FALSE, echo=CODE}
GraphIntBy10Mic3 <- ggboxplot(DATA_RECOVERY,
                            x = "Spec",
                            y = "IntBy10Mic3",
                            color = "Spec",
                            palette = "jco",
                            add = "jitter") + 
  labs(x = "Strain", y = "Mitosox signal by 1000 µm³") + 
  scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu")) + 
  stat_summary(fun.y = mean,
               geom = "point",
               shape = 20,
               size = 10,
               color = "grey",
               fill = "grey") + 
  theme(panel.background = element_rect(fill = "white", 
                                        colour = "black"),
        legend.position = "none",
        legend.text = element_text(size = 24),
        text = element_text(size = 24),
        plot.title = element_text(hjust = 0.5)) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  ylim(0,4e+08)

theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + 
  plot(GraphIntBy10Mic3)

Awake.labs <- c("After", "Before")

names(Awake.labs) <- c("After", "Before")

GraphIntBy10Mic3T <- GraphIntBy10Mic3 + 
     facet_grid(. ~ factor(Awake, 
                           levels = c('Before', 'After')), 
                labeller = labeller (Awake = Awake.labs)) + 
  theme(strip.background = element_rect(colour = "black", 
                                        fill = "white"))
plot(GraphIntBy10Mic3T)
```