---
title: "Untitled"
author: "A Dussutour / H Desgrez Dautet"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(lme4)
library(car) 
library(multcomp)
library(ggplot2)
library(MuMIn)
library(nlme)
library(lattice)
library(MASS)
library(emmeans)
library(gridExtra)
library(sjPlot)
library(sjmisc)
library(xtable)
library("ggpubr")
library(bestNormalize)
library(gridExtra)
library(grid)
library("dplyr")
library(lmerTest)
library(ggpubr)
library(unmarked)
library(AICcmodavg)

```
#open file : Data_hermes_Age.txt
Ouvre le fichier (.txt en tableau séparé par des tabulation)
```{r }
DATA_AGE <- read.table(file.choose(), header = TRUE)
str(DATA_AGE)
```

#plot data distribution and normality test, variable nucByMic3
1. distribution du nombre de noyau/mic3
2. visualisation obs/théorique
3. test de Shapiro (nb de noyaux / micron)
```{r }
ggdensity(DATA_AGE$nucByMic3, 
			 main = "Density plot for the number of nuclei by µm³", 
			 xlab = "Number of nuclei by µm³")
ggqqplot(DATA_AGE$nucByMic3)
shapiro.test(DATA_AGE$nucByMic3)
```

#normalize variable nucByMic3
1. best normalize -> transformation de la donnée pour normaliser sélectionnée selon le Pearson test
2. truehist *2 pour montrer l'avant après normalisation
3. boxplot sur les prédiction hors échantillon
```{r }
bestNormalize(DATA_AGE$nucByMic3, allow_orderNorm = FALSE)
nucByMic3BN <- bestNormalize(DATA_AGE$nucByMic3)
MASS::truehist(DATA_AGE$nucByMic3)
MASS::truehist(nucByMic3BN$x.t)
DATA_AGE$nucByMic3.t <- nucByMic3BN$x.t
boxplot(log10(nucByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable nucByMic3
vérification normalité sur les données transformées
```{r }
ggdensity(DATA_AGE$nucByMic3.t, 
          main = "Density plot for the number of nuclei by µm³ Normalized", 
          xlab = "Number of nuclei by µm³ (Normalized)")
ggqqplot(DATA_AGE$nucByMic3.t)
shapiro.test(DATA_AGE$nucByMic3.t)
```

#run LMM , variable nucByMic3 normalized
création de 2 modèles mixtes linéaires 
AnOVa sur les deux modèles (j'ai rajouté le refit = FALSE sinon l'anova faisait un refit en ML)
```{r }
ModelnucByMic3 <- lmer(nucByMic3.t~AgeW*Spec+(1|ID2),data = DATA_AGE)
summary(ModelnucByMic3)
ModelnucByMic3_2 <- lmer(nucByMic3.t~AgeW+Spec+(1|ID2),data = DATA_AGE)
summary(ModelnucByMic3_2)
anova(ModelnucByMic3,ModelnucByMic3_2, test = 'F', refit = FALSE)
```

#figure it
```{r }

tab_model(
   ModelnucByMic3_2,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Number of nuclei by Î¼mÂ³ (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu")
)
plot(ModelnucByMic3_2)
par(mfrow = c(1, 2))
ranef(ModelnucByMic3_2)
qqnorm(ranef(ModelnucByMic3_2)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelnucByMic3_2), main = "Residuals")
```

#Graph, variable nucByMic3
```{r }
GraphnucByMic3 <- ggboxplot(
   DATA_AGE,
   x = "Spec",
   y = "nucByMic3",
   color = "Spec",
   palette = "jco",
   add = "jitter"
)
+labs(x = "Strain", y = "Number of nuclei by µm³")
+scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+plot(GraphnucByMic3)

AgeW.labs <- c("1 week", "52 weeks")
names(AgeW.labs) <- c("1", "52")
GraphnucByMic3T <-GraphnucByMic3 
+facet_grid(. ~ AgeW, labeller = labeller(AgeW = AgeW.labs))
+theme(strip.background = element_rect(colour = "black", fill = "white"))

plot(GraphnucByMic3T)
```

#plot data distribution and normality test, variable MitoByMic3
```{r }
ggdensity(DATA_AGE$MitoByMic3, main = "Density plot for the number of mitochondria by µm³", xlab = "Number of mitochondria by µm³")

ggqqplot(DATA_AGE$MitoByMic3)
shapiro.test(DATA_AGE$MitoByMic3)
```

#normalize variable MitoByMic3
```{r }
bestNormalize(DATA_AGE$MitoByMic3,allow_orderNorm = FALSE)
MitoByMic3BN <- bestNormalize(DATA_AGE$MitoByMic3)
MASS::truehist(DATA_AGE$MitoByMic3)
MASS::truehist(MitoByMic3BN$x.t)
DATA_AGE$MitoByMic3.t <- MitoByMic3BN$x.t  
boxplot(log10(MitoByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1,.5, 1, 2, 5, 10)), labels = c(.1,.5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable MitoByMic3
```{r }
ggdensity(DATA_AGE$MitoByMic3.t, main = "Density plot for the number of mitochondria by µm³", xlab = "Number of mitochondria by µm³ (Normalized)")

ggqqplot(DATA_AGE$MitoByMic3.t)
shapiro.test(DATA_AGE$MitoByMic3.t)
```

#run LMM , variable MitoByMic3 normalized
```{r }
ModelMitoByMic3 <-
   lmer(MitoByMic3.t ~ AgeW * Spec +(1 | ID2), data = DATA_AGE)
summary(ModelMitoByMic3)
ModelMitoByMic3_2 <-
   lmer(MitoByMic3.t ~ AgeW +Spec +(1 | ID2), data = DATA_AGE)
summary(ModelMitoByMic3_2)
anova(ModelMitoByMic3, ModelMitoByMic3_2, test = 'F')

anova(ModelMitoByMic3, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelMitoByMic3,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Number of mitochondria by µm³ (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu", "Age x Strain")
)

plot(ModelMitoByMic3)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelMitoByMic3)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelMitoByMic3), main = "Residuals")
```

#Graph, variable MitoByMic3
```{r }
GraphMitoByMic3 <-
   ggboxplot(
      DATA_AGE,
      x = "Spec",
      y = "MitoByMic3",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Number of mitochondria by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphMitoByMic3)

AgeW.labs <- c("1 week", "52 weeks")
names(AgeW.labs) <- c("1", "52")
GraphMitoByMic3T <-
   GraphMitoByMic3 + facet_grid(. ~ AgeW, labeller = labeller (AgeW = AgeW.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))

plot(GraphMitoByMic3T)
```

#plot data distribution and normality test, variable meanAreaNuc
```{r }
ggdensity(DATA_AGE$meanAreaNuc,
          main = "Density plot for Mean Area of a Nucleus by µm³",
          xlab = "Mean Area of a Nucleus")
ggqqplot(DATA_AGE$meanAreaNuc)
shapiro.test(DATA_AGE$meanAreaNuc)
```

#normalize variable meanAreaNuc
```{r }
bestNormalize(DATA_AGE$meanAreaNuc, allow_orderNorm = FALSE)
meanAreaNucBN <- bestNormalize(DATA_AGE$meanAreaNuc)
MASS::truehist(DATA_AGE$meanAreaNuc)
MASS::truehist(meanAreaNucBN$x.t)
DATA_AGE$meanAreaNuc.t <- meanAreaNucBN$x.t
boxplot(log10(meanAreaNucBN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable meanAreaNuc
```{r }
ggdensity(DATA_AGE$meanAreaNuc.t,
          main = "Density plot for the Mean Area of a Nucleus Normalized",
          xlab = "Mean Area of a Nucleus (Normalized)")
ggqqplot(DATA_AGE$meanAreaNuc.t)
shapiro.test(DATA_AGE$meanAreaNuc.t)
```

#run LMM , variable meanAreaNuc normalized
```{r }
ModelmeanAreaNuc <- lmer(meanAreaNuc.t ~ AgeW * Spec + (1 |
                                                           ID2), data = DATA_AGE)
summary(ModelmeanAreaNuc)
ModelmeanAreaNuc_2 <-
   lmer(meanAreaNuc.t ~ AgeW + Spec + (1 | ID2), data = DATA_AGE)
summary(ModelmeanAreaNuc_2)
anova(ModelmeanAreaNuc, ModelmeanAreaNuc_2, test = 'F')

anova(ModelmeanAreaNuc, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelmeanAreaNuc,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Area of a Nucleus (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu", "Age x Strain")
)

plot(ModelmeanAreaNuc)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelmeanAreaNuc)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelmeanAreaNuc), main = "Residuals")
```

#Graph, variable meanAreaNuc
```{r }
GraphmeanAreaNuc <-
   ggboxplot(
      DATA_AGE,
      x = "Spec",
      y = "meanAreaNuc",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Area of a Nucleus")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + plot(GraphmeanAreaNuc)
AgeW.labs <- c("1 week", "52 weeks")
names(AgeW.labs) <- c("1", "52")
GraphmeanAreaNucT <-
   GraphmeanAreaNuc + facet_grid(. ~ AgeW, labeller = labeller (AgeW = AgeW.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphmeanAreaNucT)
```

#plot data distribution and normality test, variable IntByMic3
```{r }
ggdensity(DATA_AGE$IntByMic3, main = "Density plot for Mitosox signal by µm³", xlab = "Mitosox signal by µm³")
ggqqplot(DATA_AGE$IntByMic3)
shapiro.test(DATA_AGE$IntByMic3)
```

#normalize variable IntByMic3
```{r }
bestNormalize(DATA_AGE$IntByMic3, allow_orderNorm = FALSE)
IntByMic3BN <- bestNormalize(DATA_AGE$IntByMic3)
MASS::truehist(DATA_AGE$IntByMic3)
MASS::truehist(IntByMic3BN$x.t)
DATA_AGE$IntByMic3.t <- IntByMic3BN$x.t
boxplot(log10(IntByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntByMic3
```{r }
ggdensity(DATA_AGE$IntByMic3.t, main = "Density plot for the Mitosox signal by µm³ Normalized", xlab = "Mitosox signal by µm³ (Normalized)")

ggqqplot(DATA_AGE$IntByMic3.t)
shapiro.test(DATA_AGE$IntByMic3.t)
```

#run LMM , variable IntByMic3 normalized
```{r }
ModelIntByMic3 <- lmer(IntByMic3.t ~ AgeW * Spec + (1 | ID2), data = DATA_AGE)
summary(ModelIntByMic3)
ModelIntByMic3_2 <- lmer(IntByMic3.t ~ AgeW + Spec + (1 | ID2), data = DATA_AGE)
summary(ModelIntByMic3_2)
anova(ModelIntByMic3, ModelIntByMic3_2, test = 'F')

anova(ModelIntByMic3, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelIntByMic3,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Mitosox signal by µm³ (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu", "Age x Strain")
)

plot(ModelIntByMic3)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelIntByMic3)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelIntByMic3), main = "Residuals")
```

#Graph, variable IntByMic3
```{r }
GraphIntByMic3 <-
   ggboxplot(
      DATA_AGE,
      x = "Spec",
      y = "IntByMic3",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Mitosox signal by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphIntByMic3)

AgeW.labs <- c("1 week", "52 weeks")
names(AgeW.labs) <- c("1", "52")
GraphIntByMic3T <-
   GraphIntByMic3 + facet_grid(. ~ AgeW, labeller = labeller (AgeW = AgeW.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))

plot(GraphIntByMic3T)
```

#plot data distribution and normality test, variable IntMeanRescale
```{r }
ggdensity(DATA_AGE$IntMeanRescale, main = "Density plot for Mitosox signal by µm³", xlab = "Mitosox signal by µm³")
ggqqplot(DATA_AGE$IntMeanRescale)
shapiro.test(DATA_AGE$IntMeanRescale)
```

#normalize variable IntMeanRescale
```{r }
bestNormalize(DATA_AGE$IntMeanRescale, allow_orderNorm = FALSE)
IntMeanRescaleBN <- bestNormalize(DATA_AGE$IntMeanRescale)
MASS::truehist(DATA_AGE$IntMeanRescale)
MASS::truehist(IntMeanRescaleBN$x.t)
DATA_AGE$IntMeanRescale.t <- IntMeanRescaleBN$x.t
boxplot(log10(IntMeanRescaleBN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntMeanRescale
```{r }
ggdensity(DATA_AGE$IntMeanRescale.t, main = "Density plot for the Mitosox signal by µm³ Normalized", xlab = "Mitosox signal by µm³ (Normalized)")
ggqqplot(DATA_AGE$IntMeanRescale.t)
shapiro.test(DATA_AGE$IntMeanRescale.t)
```

#run LMM , variable IntMeanRescale normalized
```{r }
ModelIntMeanRescale <-
   lmer(IntMeanRescale.t ~ AgeW * Spec + (1 | ID2), data = DATA_AGE)
summary(ModelIntMeanRescale)
ModelIntMeanRescale_2 <-
   lmer(IntMeanRescale.t ~ AgeW + Spec + (1 | ID2), data = DATA_AGE)
summary(ModelIntMeanRescale_2)
anova(ModelIntMeanRescale, ModelIntMeanRescale_2, test = 'F')

anova(ModelIntMeanRescale, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelIntMeanRescale,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Mitosox signal by µm³ (Normalized)",
   pred.labels = c("Intersection", "Age", "Lu vs Malu", "Age x Strain")
)

plot(ModelIntMeanRescale)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelIntMeanRescale)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelIntMeanRescale), main = "Residuals")
```

#Graph, variable IntMeanRescale
```{r }
GraphIntMeanRescale <-
   ggboxplot(
      DATA_AGE,
      x = "Spec",
      y = "IntMeanRescale",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Mitosox signal by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
   + theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
   )
   theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()
   )
   + plot(GraphIntMeanRescale)
   AgeW.labs <- c("1 week", "52 weeks")
   names(AgeW.labs) <- c("1", "52")
   GraphIntMeanRescaleT <- GraphIntMeanRescale
   + facet_grid(. ~ AgeW, labeller = labeller (AgeW = AgeW.labs))
   + theme(strip.background = element_rect(
      colour = "black", fill = "white"
   ))
   plot(GraphIntMeanRescaleT
   )
```


#RECOVERY

#open file : Data_hermes_Recovery.txt
```{r }
DATA_RECOVERY <- read.table(file.choose(), header = TRUE)
str(DATA_RECOVERY)
```

#plot data distribution and normality test, variable nucByMic3
```{r }
ggdensity(DATA_RECOVERY$nucByMic3, main = "Density plot for the number of nuclei by µm³", xlab = "Number of nuclei by µm³")
ggqqplot(DATA_RECOVERY$nucByMic3)
shapiro.test(DATA_RECOVERY$nucByMic3)
```

#normalize variable nucByMic3
```{r }
bestNormalize(DATA_RECOVERY$nucByMic3, allow_orderNorm = FALSE)
nucByMic3BN <- bestNormalize(DATA_RECOVERY$nucByMic3)
MASS::truehist(DATA_RECOVERY$nucByMic3)
MASS::truehist(nucByMic3BN$x.t)
DATA_RECOVERY$nucByMic3.t <- nucByMic3BN$x.t
boxplot(log10(nucByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable nucByMic3
```{r }
ggdensity(DATA_RECOVERY$nucByMic3.t, main = "Density plot for the number of nuclei by µm³ Normalized", xlab = "Number of nuclei by µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$nucByMic3.t)
shapiro.test(DATA_RECOVERY$nucByMic3.t)
```

#run LMM , variable nucByMic3 normalized
```{r }
ModelnucByMic3 <-
   lmer(nucByMic3.t ~ Awake * Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelnucByMic3)
ModelnucByMic3_2 <-
   lmer(nucByMic3.t ~ Awake + Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelnucByMic3_2)
anova(ModelnucByMic3, ModelnucByMic3_2, test = 'F')

tab_model(
   ModelnucByMic3,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Number of nuclei by µm³ (Normalized)",
   pred.labels = c("Intersection", "Recovery", "Lu vs Malu", "Recovery x Strain")
)

plot(ModelnucByMic3_2)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelnucByMic3_2)$ID2[, 1],
       main = "Random effects of ID")
qqnorm(resid(ModelnucByMic3_2), main = "Residuals")
```

#Graph, variable nucByMic3
```{r }
GraphnucByMic3 <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "nucByMic3",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   ) + labs(x = "Strain", y = "Number of nuclei by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphnucByMic3)
Awake.labs <- c("Before", "After")
names(Awake.labs) <- c("Before", "After")
GraphnucByMic3T <- GraphnucByMic3
+ facet_grid(. ~ factor(Awake, levels = c('Before', 'After')), labeller = labeller (Awake =
                                                                                       Awake.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphnucByMic3T)
```

#plot data distribution and normality test, variable MitoByMic3
```{r }
ggdensity(DATA_RECOVERY$MitoByMic3, main = "Density plot for the number of mitochondria by µm³", xlab = "Number of mitochondria by µm³")
ggqqplot(DATA_RECOVERY$MitoByMic3)
shapiro.test(DATA_RECOVERY$MitoByMic3)
```

#normalize variable MitoByMic3
```{r }
bestNormalize(DATA_RECOVERY$MitoByMic3, allow_orderNorm = FALSE)
MitoByMic3BN <- bestNormalize(DATA_RECOVERY$MitoByMic3)
MASS::truehist(DATA_RECOVERY$MitoByMic3)
MASS::truehist(MitoByMic3BN$x.t)
DATA_RECOVERY$MitoByMic3.t <- MitoByMic3BN$x.t
boxplot(log10(MitoByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable MitoByMic3
```{r }
ggdensity(DATA_RECOVERY$MitoByMic3.t, main = "Density plot for the number of mitochondria by µm³", xlab = "Number of mitochondria by µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$MitoByMic3.t)
shapiro.test(DATA_RECOVERY$MitoByMic3.t)
```

#run LMM , variable MitoByMic3 normalized
```{r }
ModelMitoByMic3 <-
   lmer(MitoByMic3.t ~ Awake * Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelMitoByMic3)
ModelMitoByMic3_2 <-
   lmer(MitoByMic3.t ~ Awake + Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelMitoByMic3_2)
anova(ModelMitoByMic3, ModelMitoByMic3_2, test = 'F')

anova(ModelMitoByMic3_2, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelMitoByMic3_2,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Number of mitochondria by µm³ (Normalized)",
   pred.labels = c("Intersection", "Recovery", "Lu vs Malu")
)

plot(ModelMitoByMic3_2)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelMitoByMic3_2)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelMitoByMic3_2), main = "Residuals")
```

#Graph, variable MitoByMic3
```{r }
GraphMitoByMic3 <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "MitoByMic3",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   ) + labs(x = "Strain", y = "Number of mitochondria by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphMitoByMic3)
Awake.labs <- c("Before", "After")
names(Awake.labs) <- c("Before", "After")
GraphMitoByMic3T <- GraphMitoByMic3
+ facet_grid(. ~ factor(Awake, levels = c('Before', 'After')), labeller = labeller (Awake =
                                                                                       Awake.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphMitoByMic3T)
```

#plot data distribution and normality test, variable meanAreaNuc
```{r }
ggdensity(DATA_RECOVERY$meanAreaNuc, main = "Density plot for Mean Area of a Nucleus by µm³", xlab = "Mean Area of a Nucleus")
ggqqplot(DATA_RECOVERY$meanAreaNuc)
shapiro.test(DATA_RECOVERY$meanAreaNuc)
```

#normalize variable meanAreaNuc
```{r }
bestNormalize(DATA_RECOVERY$meanAreaNuc, allow_orderNorm = FALSE)
meanAreaNucBN <- bestNormalize(DATA_RECOVERY$meanAreaNuc)
MASS::truehist(DATA_RECOVERY$meanAreaNuc)
MASS::truehist(meanAreaNucBN$x.t)
DATA_RECOVERY$meanAreaNuc.t <- meanAreaNucBN$x.t
boxplot(log10(meanAreaNucBN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable meanAreaNuc
```{r }
ggdensity(DATA_RECOVERY$meanAreaNuc.t,
          main = "Density plot for the Mean Area of a Nucleus Normalized",
          xlab = "Mean Area of a Nucleus (Normalized)")
ggqqplot(DATA_RECOVERY$meanAreaNuc.t)
shapiro.test(DATA_RECOVERY$meanAreaNuc.t)
```

#run LMM , variable meanAreaNuc normalized
```{r }
ModelmeanAreaNuc <-
   lmer(meanAreaNuc.t ~ Awake * Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelmeanAreaNuc)
ModelmeanAreaNuc_2 <-
   lmer(meanAreaNuc.t ~ Awake + Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelmeanAreaNuc_2)
anova(ModelmeanAreaNuc, ModelmeanAreaNuc_2, test = 'F')

anova(ModelmeanAreaNuc_2, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelmeanAreaNuc_2,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Area of a Nucleus (Normalized)",
   pred.labels = c("Intersection", "Recovery", "Lu vs Malu")
)

plot(ModelmeanAreaNuc_2)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelmeanAreaNuc_2)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelmeanAreaNuc_2), main = "Residuals")
```

#Graph, variable meanAreaNuc
```{r }
GraphmeanAreaNuc <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "meanAreaNuc",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Area of a Nucleus")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphmeanAreaNuc)
Awake.labs <- c("After", "Before")
names(Awake.labs) <- c("After", "Before")
GraphmeanAreaNucT <- GraphmeanAreaNuc
+ facet_grid(. ~ factor(Awake, levels = c('Before', 'After')), labeller = labeller (Awake =
                                                                                       Awake.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphmeanAreaNucT)
```

#plot data distribution and normality test, variable IntByMic3
```{r }
ggdensity(DATA_RECOVERY$IntByMic3, main = "Density plot for Mitosox signal by µm³", xlab = "Mitosox signal by µm³")
ggqqplot(DATA_RECOVERY$IntByMic3)
shapiro.test(DATA_RECOVERY$IntByMic3)
```

#normalize variable IntByMic3
```{r }
bestNormalize(DATA_RECOVERY$IntByMic3, allow_orderNorm = FALSE)
IntByMic3BN <- bestNormalize(DATA_RECOVERY$IntByMic3)
MASS::truehist(DATA_RECOVERY$IntByMic3)
MASS::truehist(IntByMic3BN$x.t)
DATA_RECOVERY$IntByMic3.t <- IntByMic3BN$x.t
boxplot(log10(IntByMic3BN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntByMic3
```{r }
ggdensity(DATA_RECOVERY$IntByMic3.t, main = "Density plot for the Mitosox signal by µm³ Normalized", xlab = "Mitosox signal by µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$IntByMic3.t)
shapiro.test(DATA_RECOVERY$IntByMic3.t)
```

#run LMM , variable IntByMic3 normalized
```{r }
ModelIntByMic3 <-
   lmer(IntByMic3.t ~ Awake * Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelIntByMic3)
ModelIntByMic3_2 <-
   lmer(IntByMic3.t ~ Awake + Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelIntByMic3_2)
anova(ModelIntByMic3, ModelIntByMic3_2, test = 'F')

anova(ModelIntByMic3, type = 3, ddf = "Satterthwaite")

tab_model(
   ModelIntByMic3,
   show.df = TRUE,
   show.stat = TRUE,
   show.loglik = TRUE,
   dv.labels = "Mitosox signal by µm³ (Normalized)",
   pred.labels = c("Intersection", "Recovery", "Lu vs Malu", "Recovery x Strain")
)

plot(ModelIntByMic3)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelIntByMic3)$ID2[, 1],
       main = "Random effects of ID")
qqnorm(resid(ModelIntByMic3), main = "Residuals")
```

#Graph, variable IntByMic3
```{r }
GraphIntByMic3 <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "IntByMic3",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Mitosox signal by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphIntByMic3)
Awake.labs <- c("After", "Before")
names(Awake.labs) <- c("After", "Before")
GraphIntByMic3T <-
   GraphIntByMic3 + facet_grid(. ~ factor(Awake, levels = c('Before', 'After')), labeller = labeller (Awake =
                                                                                                         Awake.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphIntByMic3T)
```

#plot data distribution and normality test, variable IntMeanRescale
```{r }
ggdensity(DATA_RECOVERY$IntMeanRescale,
          main = "Density plot for Mitosox signal by µm³",
          xlab = "Mitosox signal by µm³")
ggqqplot(DATA_RECOVERY$IntMeanRescale)
shapiro.test(DATA_RECOVERY$IntMeanRescale)
```

#normalize variable IntMeanRescale
```{r }
bestNormalize(DATA_RECOVERY$IntMeanRescale, allow_orderNorm = FALSE)
IntMeanRescaleBN <- bestNormalize(DATA_RECOVERY$IntMeanRescale)
MASS::truehist(DATA_RECOVERY$IntMeanRescale)
MASS::truehist(IntMeanRescaleBN$x.t)
DATA_RECOVERY$IntMeanRescale.t <- IntMeanRescaleBN$x.t
boxplot(log10(IntMeanRescaleBN$oos_preds), yaxt = 'n')
axis(2, at = log10(c(.1, .5, 1, 2, 5, 10)), labels = c(.1, .5, 1, 2, 5, 10))
```

#plot normalized data distribution and normality, variable IntMeanRescale
```{r }
ggdensity(DATA_RECOVERY$IntMeanRescale.t,
          main = "Density plot for the Mitosox signal by µm³ Normalized",
          xlab = "Mitosox signal by µm³ (Normalized)")
ggqqplot(DATA_RECOVERY$IntMeanRescale.t)
shapiro.test(DATA_RECOVERY$IntMeanRescale.t)
```

#run LMM , variable IntMeanRescale normalized
```{
r
}
ModelIntMeanRescale <-
lmer(IntMeanRescale.t ~ Awake * Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelIntMeanRescale)
ModelIntMeanRescale_2 <-
lmer(IntMeanRescale.t ~ Awake + Spec + (1 | ID2), data = DATA_RECOVERY)
summary(ModelIntMeanRescale_2)
anova(ModelIntMeanRescale, ModelIntMeanRescale_2, test = 'F')

anova(ModelIntMeanRescale, type = 3, ddf = "Satterthwaite")

tab_model(
ModelIntMeanRescale,
show.df = TRUE,
show.stat = TRUE,
show.loglik = TRUE,
dv.labels = "Mitosox signal by µm³ (Normalized)",
pred.labels = c("Intersection", "Recovery", "Lu vs Malu", "Recovery x Strain")
)

plot(ModelIntMeanRescale)
par(mfrow = c(1, 2))
qqnorm(ranef(ModelIntMeanRescale)$ID2[, 1], main = "Random effects of ID")
qqnorm(resid(ModelIntMeanRescale), main = "Residuals")
```

#Graph, variable IntMeanRescale
```{r }
GraphIntMeanRescale <-
   ggboxplot(
      DATA_RECOVERY,
      x = "Spec",
      y = "IntMeanRescale",
      color = "Spec",
      palette = "jco",
      add = "jitter"
   )
+ labs(x = "Strain", y = "Mitosox signal by µm³")
+ scale_x_discrete(breaks = c("Lu", "MaLu"),
                   labels = c("Lu", "Malu"))
+ stat_summary(
   fun.y = mean,
   geom = "point",
   shape = 20,
   size = 10,
   color = "grey",
   fill = "grey"
)
+ theme(
   panel.background = element_rect(fill = "white", colour = "black"),
   legend.position = "none",
   legend.text = element_text(size = 24),
   text = element_text(size = 24),
   plot.title = element_text(hjust = 0.5)
)
+ theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank())
+ plot(GraphIntMeanRescale)
Awake.labs <- c("After", "Before")
names(Awake.labs) <- c("After", "Before")
GraphIntMeanRescaleT <-
   GraphIntMeanRescale + facet_grid(. ~ ~ factor(Awake, levels = c('Before', 'After')), labeller = labeller (Awake =
                                                                                                                Awake.labs))
+ theme(strip.background = element_rect(colour = "black", fill = "white"))
plot(GraphIntMeanRescaleT)
```




